### 2023-09-07 main.tex
jkl

@@

@@

@@

Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j,k\in\{1,\ldots,N-1\}$
\begin{equation}\label{Three-Relation}
	Q_{0}^{2L}B_{k}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}B_{k}^{2L-1}\prod_{j=}^{3}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
Observe that \eqref{Three-Relation} also implies that 

@@

		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&
		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle

>>>>

\begin{equation}\label{Dij-ref}

@@

\begin{equation}\label{DijBk-different}

@@

\begin{equation}\label{Dii-ref}

@@

Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j\in\{1,\ldots,N-1\}$
\begin{equation}\label{Two-Relation}
	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
Indeed, consider \eqref{ExQ0B-charges} then we can write 
	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle
Using \eqref{Dij-ref}, and \eqref{Dii-ref} we obtain 
	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)\right\}|\Psi_{0}^{0}\rangle
Now two different cases are possible:
	\item \textit{Case 1}: $i=j$ therefore using \eqref{DijBk-different} we obtain 
		&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
		B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
Using again 
Observe that \eqref{Two-Relation} also implies that 

@@

		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}\\&
		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
